---
title: "Macropis nuda & Dufourea novaeangliae SDM"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(raster)
library(leaflet)
library(htmlwidgets)
library(htmltools)
library(wesanderson)

#Load Rasters
mn <- raster("../MnDn_ENM/Data/Pred/predictions/Mn/Mn_SDM_ME_1km_p10.tif")
dn <- raster("../MnDn_ENM/Data/Pred/predictions/Dn/Dn_SDM_ME_1km_p10.tif")

#Tag with CRS
crs(mn) <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
crs(dn) <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

#Color palettes 
pal <- as.character(wes_palette("Zissou1"))
pal2 <- as.character(wes_palette("FantasticFox1")[c(3,2,4,1,5)])

pal.mn <- colorNumeric(palette = pal, values(mn),
                    na.color = "transparent")

pal.dn <- colorNumeric(palette = pal, values(dn),
                    na.color = "transparent")
```

Species Distribution Models (SDMs) for *Macropis nuda* and *Dufourea novaeangliae* created with MaxEnt using a 10th percentile threshold. All levels of suitability correspond to a prediction of species presence (Note: the presence threshold differs between each species). Red grid cells are predicted to be the most suitable given the available occurrence data and predictors used. 

Approx. 1km resolution

```{r, echo=FALSE, warning=FALSE, out.width= "120%", fig.height= 9}
map <- leaflet(options = leafletOptions(minZoom = 7.3)) %>% addTiles() %>%
  addProviderTiles(providers$OpenStreetMap, group = "Street") %>% 
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%
  addProviderTiles(providers$Esri.WorldTopoMap, group = "Topo") %>% 
  addRasterImage(mn, colors = pal.mn, opacity = 0.50, group = "M. nuda") %>%
  addRasterImage(dn, colors = pal.dn, opacity = 0.50, group = "D. novaeangliae") %>% 
  addLegend(pal = pal.mn, values = values(mn),
            title = "Suitability",
            opacity = 1,
            group = "M. nuda") %>% 
  addLegend(pal = pal.dn, values = values(dn),
            title = "Suitability",
            opacity = 1,
            group = "D. novaeangliae") %>%
  setMaxBounds( lng1 = -80
                , lat1 = 40
                , lng2 = -70
                , lat2 = 46) %>% 
  fitBounds( lng1 = -75
                , lat1 = 40
                , lng2 = -70
                , lat2 = 46) %>% 
  #addControl(title, position = "topleft", className="map-title") %>% 
  addMiniMap(
    tiles = providers$CartoDB.Positron,
    toggleDisplay = TRUE,
    zoomAnimation = TRUE,
    aimingRectOptions = list(weight = 2.5, clickable = TRUE),
    minimized = TRUE) %>% 
  addLayersControl(
    baseGroups = c("Street", "Satellite", "Topo"),
    overlayGroups = c("M. nuda", "D. novaeangliae"),
    options = layersControlOptions(collapsed = FALSE),
    position = "bottomleft")

map
```
